---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/traitecoevo/rmot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/traitecoevo/rmot/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/fontikar/augGauss/branch/master/graph/badge.svg)](https://app.codecov.io/gh/traitecoevo/rmot?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

# augGauss

R package to analyse generalisation gradients using Stan.

The goal of 'augGauss' is to provide a way to analyse gradients of generalised responding along a continuous stimulus dimension. The hierarchical model fits an "augmented" Gaussian function to individual generalisation gradients and estimates descriptive parameters. The augmented Gaussian is a Gaussian function with two width parameters that allow the function to be asymmetrical. The package uses Stan to estimate posterior distributions for 4 parameters: mean (location of the gradient peak on the stimulus dimension), height (the height of the peak), and two width parameters (width- and width+ for the left, and right sides of the gradient).

## Installation

'augGauss' is under active development. You can install the current developmental version of 'augGauss' from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("fontikar/augGauss")
```

We recommend checking out the vignette to get started: 

```{r}
vignette("augGauss")
```


## Found a bug? 

Please submit a [GitHub issue](https://github.com/traitecoevo/rmot/issues) with details of the bug. A [reprex](https://reprex.tidyverse.org/) would be particularly helpful with the bug-proofing process!  
