---
title: "augGauss"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{augGauss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(augGauss)
```

## Goal of package

## Installation

'augGauss' is under active development, you can install the development version of 'augGauss' from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("traitecoevo/augGauss")

library(augGauss)
```

## Getting started

We will be using some example data to demonstrate the main functions of `augGauss`

```{r}
demo_data

?demo_data
```

## Simulate gradients from raw data

```{r}
sim_data <- simulate_data(nSubj = 10, nGroups = 3)

sim_data
```

You can save the simulated data by setting the `save_data` argument to `TRUE`

```{r, eval=FALSE}
sim_data <- simulate_data(nSubj = 10, nGroups = 3, save_data = TRUE)
```

## Template for model

<!-- Need info from JL about what are the parameters that we feed data into -->

```{r}
aug_model("gaussian")
```


